\large Autonomous Aerial Exploration for Topological Mapping of Mars Environments

### 2019-01-10 Dissertation/Defense/scitech19_presentation.tex
minor edits to prepresentation

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Topography of Mars
	\begin{itemize}
		\item Future mission planning
		\item Spacecraft landing
		\item Image distortion correction
		\item The Mars Orbiting Laser Altimeter (MOLA) uncertainty is about $8$ meters
	\end{itemize}
	\pause
	\item Mars Rovers for Mapping Mars
	\begin{itemize}
		\item Four successful driving missions, Curiosity still functional and communicating
		\item Driving robots are incapable of traversing steep or dangerous terrain
		\item Humans cannot control rovers directly due to a time delay from Earth
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{itemize}
	\item Bayesian Framework
	\begin{itemize}
	\item Markov Assumption: latest a priori cell occupancy probabilities capture the information from all prior observations
	\item Log-Odds Ratio: popular representation due to simple additive update structure and probability truncation avoidance, but requires the \emph{assumption}
	\begin{align*}
		P(Z_t|\mathbf{m}_i,X_{1:t},Z_{1:t-1})\approx P(Z_t|\mathbf{m}_i,X_t)
	\end{align*}
	\end{itemize}
\vspace*{0.0cm}\pause
	\item Inverse Sensor Model
	\begin{align*}
&P(\mathbf{m}_i|z_{t,l},X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l}\sum_{m\in\mathcal{M}_i}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}).
\end{align*}
	\begin{itemize}
	\item Given $n$ grid cells: $\mathcal O(2^n)$ is \emph{computationally-intractable}, motivating a different solution
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item Using the cost map from before, \emph{Dijkstra's algorithm} is completed by finding the waypoints from the desired candidate back to the current location
	\vspace*{0.0cm}\pause
	\item These waypoints serve as input to a \emph{constrained polynomial least squares trajectory}
	\begin{itemize}
		\item Each trajectory is solved independently as a function of time, i.e. $x(t)$, $y(t)$
		\item Starting and terminal locations are fixed
		\item Segments patched together have the same position and velocity at the connection
	\end{itemize}
	\vspace*{0.0cm}\pause
	\item A \emph{geometric controller} tracks the trajectory without \emph{singularities} or \emph{ambiguities}
	\vspace*{0.0cm}\pause
	\item The mapping, exploration, and control run in \emph{real-time}
\end{itemize}

@@

\begin{itemize}
	\item Apply Dijkstra's algorithm about 3D graph of occupancy grid
	\item Locations and associated distance costs for reachable positions in 3D
\end{itemize}
\begin{figure}
	\centering
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{mars_closeup.png}
        		\caption{Mars Simulation Poses}
    	\end{subfigure}
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{connected_costmap.png}
        		\caption{3D Dijkstra's Search}
    	\end{subfigure}
\label{fig:marsZoomedIn}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Experiment Summary}
\begin{itemize}
        	\item Environments in complex 3D are modeled with occupancy grids in simulation and experimentation
	\item Predicted entropy of certain and uncertain spaces provide a policy for 3D autonomous exploration
	\item Dijkstra's search provides a collision-free path and estimated travel costs that account for obstacles
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
        	\item Proposed an occupancy grid mapping technique that uses the \emph{exact probabilistic solution}
	\item Computational cost is reduced \emph{substantially} for \emph{real-time implementation} using probabilisitic properties and exploiting mathematical patterns
	\item Exact mapping concepts are extended to map uncertainty to accomplish \emph{autonomous exploration}
	\item Multiple vehicles can explore and patrol an uncertain environment using a \emph{bidding}-based approach
	\item These are demonstrated with numerous simulations and experiments
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Topography of Mars
	\begin{itemize}
		\item Future mission planning
		\item Spacecraft landing
		\item Image distortion correction
		\item The Mars Orbiting Laser Altimeter (MOLA) uncertainty is about $8$ meters
	\end{itemize}
	\pause
	\item Mars Rovers for Mapping Mars
	\begin{itemize}
		\item Four successful driving missions, Curiosity still functional and communicating
		\item Driving robots are incapable of traversing steep or dangerous terrain
		\item Humans cannot control rovers directly in real-time due to a time delay from Earth
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{itemize}
	\item Bayesian Framework with a Markov Assumption: latest a priori cell occupancy probabilities capture the information from all prior observations
\vspace*{0.0cm}\pause
	\item Inverse Sensor Model
	\begin{align*}
&P(\mathbf{m}_i|z_{t,l},X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l}\sum_{m\in\mathcal{M}_i}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}).
\end{align*}
	\item Given $n$ grid cells: $\mathcal O(2^n)$ is \emph{computationally-intractable}, motivating a different solution
\end{itemize}

@@

\begin{itemize}
	\item Using the cost map from before, \emph{Dijkstra's algorithm} is completed by finding the waypoints from the desired candidate back to the current location
	\vspace*{0.0cm}\pause
	\item These waypoints serve as input to a \emph{constrained polynomial least squares trajectory}
	\begin{itemize}
		\item Each trajectory is solved independently as a function of time, i.e. $x(t)$, $y(t)$, and $z(t)$
		\item Starting and terminal locations are fixed
		\item Segments patched together have the same position and velocity at the connection
	\end{itemize}
	\vspace*{0.0cm}\pause
	\item A \emph{geometric controller} tracks the trajectory without \emph{singularities} or \emph{ambiguities}
	\vspace*{0.0cm}\pause
	\item The mapping, exploration, and control run in \emph{real-time}
\end{itemize}

@@

\begin{itemize}
	\item Apply Dijkstra's algorithm about 3D graph of occupancy grid
	\item Locations and associated distance costs for reachable positions in 3D
\end{itemize}
\begin{figure}
	\centering
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{connected_costmap.png}
        		\caption{3D Dijkstra's Search}
    	\end{subfigure}
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{mars_closeup.png}
        		\caption{Mars Simulation Poses}
    	\end{subfigure}
\label{fig:marsZoomedIn}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Simulation and Experiment Summary}
\begin{itemize}
        	\item Environments in complex 3D are modeled with occupancy grids in simulation and experimentation
	\item Predicted entropy of certain and uncertain spaces provide a policy for 3D autonomous exploration
	\item Dijkstra's search provides a collision-free path and estimated travel costs that account for obstacles
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
        	\item Proposed an occupancy grid mapping technique that uses the \emph{exact probabilistic solution}
	\item Exact mapping concepts are extended to map uncertainty to accomplish \emph{autonomous exploration} for a flying vehicle above the surface of Mars
	\item These are demonstrated with a Mars simulation and a flight experiment
\end{itemize}
\end{frame}
